%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Author : [Name] [Surname], Tomas Polasek (template)
% Description : Seventh exercise in the Introduction to Game Development course.
%   It deals with the creation of a Game Design Document, presenting a short 
%   pitch for a potential game project.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[a4paper,10pt,english]{article}

\usepackage[left=2.50cm,right=2.50cm,top=1.50cm,bottom=2.50cm]{geometry}
\usepackage[utf8]{inputenc}

% Hyper-Text References
\usepackage{hyperref}
\hypersetup{colorlinks=true, urlcolor=blue}

% Drawing Images and Graphs
\usepackage{tikz}
\usepackage{pgfplots}

% Page Utilities
\usepackage{graphicx}

% Image Sub-Captions
\usepackage{subcaption}

\newcommand{\ph}[1]{\textit{[#1]}}

\title{%
Game Pitch Document%
}
\author{%
Michal Zobaník (xzoban01)%
}
\date{}

\begin{document}

\maketitle
\thispagestyle{empty}

{%
\large

\begin{itemize}

\item[] \textbf{Title:} Chronicles of extinction

\item[] \textbf{Genre:} Sandbox tower defense

\item[] \textbf{Style:} 2d pixel art

\item[] \textbf{Platform:} PC

\item[] \textbf{Market:} 13 -30 years old

\item[] \textbf{Elevator Pitch:} Open world tower defense game with live exciting world and amazing story

\end{itemize}

}

\section*{\centering The Pitch}

\subsection*{Introduction}
Chronicles of extinction is game about building your own hover ship, which is used to travel around open world to complete quest, mine resources to sell or upgrade your ship.

\subsection*{Background}
My biggest inspiration were games like Factorio or Bloons TD 6. I like tower defense and building games with managing resources. But none of games i played have all of this at once with compelling story.

\subsection*{Setting}
Game is set in postapocalyptic world on some planet somewhere in space. In the past the planet was invaded by aliens and most of the people living there were wipe out. Remaining population created heavily armed outposts, each of them is separated by destroyed world filled by dangerous aliens. You play as captain of hover ship. You as trader are traversing this dangerous world from outpost to outpost and delivering resources, peoples, killing aliens and upgrading your own ship.

\subsection*{Features}

\begin{itemize}
    \item Openworld filled with interesting and mysterous places of destroyed cities
    \item Opurtunity to build your own ship with different wepons, visuals, engines and others
    \item rich and compeling story about reclaiming and rebuilding destroyed world
    \item freedom to do what you want - gather resources, focus on combat and tower defense part, trading with outposts or completing story
\end{itemize}

\subsection*{Genre}
Tower defense game - building own ship and then defending against hordes of enemies while you travel or gather resources

\subsection*{Platform}
Game will release on PC. Later if popularity will be big enough maybe even XBOX or PS

\subsection*{Style}
Game will be 2D with pixel art graphics with darker color pallet and mostly steampunk or industrial look

\end{document}
